\chapter*{Business Information}
\addcontentsline{toc}{chapter}{Business Information}
\pagenumbering{arabic}

The purpose of this chapter is to describe the business environment of Bookflix.

\section{Business vision}
Bookflix will serve digital book to consumers for a fixed price.
The main goals of the project are:
* Provide digital book downloads
* Allow exchange of (digital) books between users

The positives and negative aspects of the system are analyzed using SWOT analyis:

Strengths
* Monthly cost 
* Access to large library of books
* Quick access to books

Weaknesses
* Digital books are purely virtual and of such ownership is less valuable than owning a physical book.
* Digital reading device necesarry

Oppertunities
* Ability to market users social groups through stored 

Threats
* Consumers not wanting to transition from fysical to digital books.
* Content providers pulling back their books from content service.


\section{Business rationale}


\section{Target audience}
The Bookflix product is targeted towards the fysical and digital book reading crowd worldwide. Sub groups within this audience are young people (<30 years), late adults (>30) and finally elderly (>60).

The younger group has a high affinity with digital devices and will most likely use many of the extra services of Bookflix.
This group also will likely interact with the application on mobile devices such as smart phones, ereaders and tablets.

The late adults are used to reading fysical books.
Extra care will be taken in the marketing to convey the possitives of digital books and special offers will be made providing digital copies along fysical products.
The latter will smooth the transition to the digital distribution for this target audience.

Finally the elderly are used to reading fysical books and have relatively low experience with digital distribution.
A small niche in this group will likely be open to the aspect of digital books.


\section{Business model}
Bookflix is a content service at it's core.
As a service Bookflix acts as a intermidiary for users to trade/rent books to other users.

Bookflix is a content service which allows easy access to ebooks for users from content providers.
Access to the Bookflix library is granted on a monthly subscription basis.
The subscription fee is a fixed price irrespective of actual usages.
However to prevent missuse of the system a fair use policy is applicable.
A free trial for the term of one month is provided for user to try the service and be persuaded to subscribe.

Individual contracts which content providers are already setup with content providers.
The costs of these contract varry per provider but generally contain a base price/month and a dynamic portion.
The dynamic contract costs are calculated by proportionaly divided 70\% of the profit among content providers according to number of books reads/downloaded for the respective provider.

As a service Bookflix will act as a broker between users to exchange fysical books.
Users can rent, trade or sell books to other users and Bookflix will govern the transaction.
A commsion of 10\% is held on transactions with a set minimum amount.
Bookflix will garantee a good transaction between users and compensate damages to seller in case of malpayment from the buyer.

\section{Roadmap}


\section{Financial Model}
